---
title: "Mini_Project_2"
format: html
editor: visual
---

Mini Project 2 Original

```{r}
library(tidyverse)
tags <- read_csv("Snow_Emergency_Northrop_Tags_2023.csv")
tows <- read_csv("Snow_Emergency_Northrop_Tows_2023.csv")



df1 <- tags |>
  inner_join(tows,by = "Day")


ggplot(data = df1) + geom_point(aes(x = Time,y = Community.y, color = Tow_Zone.x)) + facet_grid(Day ~ .) + labs(title = "Time of Towing in Communities", y = "Community", color = "Tow Zone")

#I thought that it could be interesting to see which communities are getting towed at what time. Then I slowly tried to increase the visibility of that graph. So I added the tow zone coloring and facited it all by the day.

#IDK if there are any good conclusions to come to with this data but I find the gap in the first time section of day 2 to be weird, also that Northeast and Soutwest avoided a day of citations and tows. Guess we gotta find out what their secret is!

```

Mini Project 5 (Updated version of 2)

Unfortunately I couldn't figure out how to add the title, it kept throwing errors in my addlegend :(

```{r}
library(tidyverse)
library(sf)     # R wrapper around GDAL/OGR
library(leaflet)    # for fortifying shapefiles
library(leaflet.extras)   # For leaflet heatmaps
library(ggmap)   # Making google maps

city_boundry <- st_read(dsn = "~/DST 234 Files/Mini_Project_2/City_Boundary-shp", layer = "16cdbbfa-ad10-493c-afaf-52b61f2e76e42020329-1-180h9ap.whbo")

neighborhood_boundry <- st_read(dsn = "~/DST 234 Files/Mini_Project_2/Minneapolis_Neighborhoods")

#minimaizing data, so it doesn't take years to run
df2 <- df1 |> filter(Day==1) |> filter(Ward.x!=0) |> filter(Ward.y!=0)

TagsTowsMap <- df2 |>
  leaflet() |> 
  addTiles() |>
  addPolygons(data=city_boundry,weight=5,color = "black",fill=FALSE) |>
  addPolygons(data = neighborhood_boundry,weight=1,color = "black",fillColor="black") |>
  addWebGLHeatmap(lng = ~Longitude.x,lat = ~Latitude.x,size=200,opacity = 0.8)
  #|> addLegend funtion would go here, to add the title: "Heatmap of Tags and Tows in Minneapolis" and labels: "Black = Area within Minneapolis", "Red = Areas where there was a Tag or a Tow"
  

TagsTowsMap
```

I improved my Mini-Project 2 by adding a heat map of the tags and tows to the city of Minneapolis. This is much better than what I previously had because it gives a better idea of where the tags and tows are happening during the snow plow warnings. I went from a very basic ggplot to a solid looking map. It has a border around the city of Minneapolis and each neighborhood. Areas within the city/neighborhoods are shaded black and areas with tags or tows are red!

I was rather disappointed with my original mini-project 2, but this makes me feel much better about it. This was my original idea for this mini-project but I didn't know mapping when this was an assignment! I am just glad that I got to go back and redo my project with my original idea!
