---
title: "THIS IS YOUR TITLE"
author: "ENTER YOUR NAME HERE"
date: "2023-09-13"
format:
  html:
    embed-resources: true
---

```{r}
#| echo: false

library(mdsr)
library(tidyverse)
```

## Problem 3
Download and save the file `memorization_data.csv` located on the moodle website. These data represent the time it takes to memorize a list of 20 words across 10 different rounds with 12 different participants, with the following columns:

- Round: Stage of the memorization (1 - 10)
- Words: Number of words memorized.
- Student: ID for the given student (1 - 12)
- Gender: Gender identity of student (M = male, F = female, NB = nonbinary)
- Languages: Number of languages student speaks

Using this quatro file, import this csv file into R and construct an informative data visualization from the data. 

**Note:** this dataset contains some quantitative and categorical data, so be creative in how you set up the visualization.

Type your response here, embedding documented code in the chunk below

```{r}
memorization_data <- read_csv('memorization_data.csv')

# Now make your plot!
```
```{r}
ggplot(data = memorization_data, aes(x= Words, y= Round, color = Gender, shape = Gender)) +
  geom_point() + ggtitle('Words versus Rounds split by Gender')
```

