---
title: "homework12"
format: html
editor: visual
---

Question 1: 3-4 interesting things in the readings

1.  I didn't know that there were multiple ways to remove the nulls since we have only done the rm.na = TRUE method, where in the reading they show values_drop_na = TRUE

2.  I really like the demonstration of Figure 6.7 for combining/simplifying the columns with names_to and .value

3.  I found the parentheses (2.2.2) section to be interesting. Mainly because I feel totally called out with the good vs bad example of spaces with if statements

    \# Good

    if (debug) {

    show(x)

    }

    \# Bad

    if(debug){ (I always do my if statements the bad way hahaha

    show(x)

    }

4.  This isn't necessarily a specific thing but on the style guide page 9, error messages. I really like looking through this because I always get lots of errors and this can help me

Question 2:

```{r}
library(tidyverse)
select(filter(mtcars,cyl==4),mpg,cyl)
```

I much prefer pipes, it is just easier to understand and implement. Using pipes feels more forgiving.

Question 3:

```{r}
exer6 <- tibble( grp = c("A","A","B","B"),
sex = c("F","M","F","M"),
meanL = c(0.225,0.47,0.325,0.547),
sdL = c(0.106,0.325,0.106,0.308),
 meanR = c(0.34,0.57,0.4,0.647),
sdR = c(0.0849,0.325,0.0707,0.274) )



wide <- exer6 |>
  pivot_longer(cols = -c(grp, sex), names_to = "variable", values_to = "value") |>
  unite("new_variable", c(sex, variable), sep = ".") |> 
  pivot_wider(names_from = new_variable, values_from = value)

```
