---
title: "Homework23"
format: html
editor: visual
---

## Homework 23

```{r}
library(tidyverse)
library(mosaicData)

?mosaicData::HELPrct
mosaicData::HELPrct |> glimpse()


data <- mosaicData::HELPrct
```

Question 1a:

The following variables are: age, anysubstatus, anysub, cesd, d1, daysanysub, dayslink, drugrisk, e2b, female, sex, g1b, homeless, i1, i2, id, indtot, linkstatus, link, mcs, pcs, pss_fr, racegrp, satreat, sexrisk, substance, treat, avg_drinks, max_drinks, hospitalizations

Seems like this data set contains information about drinks, drugs and the hospitalizations surrounding them related to addiction.

Question 1b:

```{r}
is.numeric(mosaicData::HELPrct$treat)
#idk what treat means even by reading the description of the data set or the column
is.numeric(mosaicData::HELPrct$max_drinks)
#this is the number of the most drinks that the person had
```

Question 1c:

```{r}

out <- vector("numeric", dim(data)[2])

for (i in seq_along(data)) {
  out[i] <- mean(data[[i]])
}

dim(data)[2]
mydata <- summary(data, na.rm=TRUE)

mydata
```

Question 1d:

```{r}
data2 <- mosaicData::HELPrct |> group_by(sex) |> nest()

out2 <- vector("numeric", dim(data2)[2])

for (i in seq_along(data2)) {
  out[i] <- mean(data2[[i]])
}

dim(data2)[2]
mydata2 <-  summary(data2)

mydata2
```
