---
title: "DST-234 Homework day 8"
format: html
editor: visual
---

## Quarto

```{r}
glimpse(babynames)
```

Problem 1a: Probably used the filter commands to remove prop

Problem 1b: Looks like they used another filter command to remove any male names

Problem 1c: I think they used mutate to add total. Or they could've used summarize to add total

Problem 1d: Seems like they used Arrange to sort the rows in ascending order

Problem 2a: doesn't look like anything is wrong, just uses the old pipeline operator

Problem 2b: Looks like they messed up in the parenthesis. They are subtracting year from nothing which shouldn't work

Problem 2c: looks correct

Problem 2d: Didn't use parenthesis around "sex == M" and also selected -prop which I don't think you can subtract something from nothing

Problem 2e: Looks right, I don't know the syntax great but it might get angry by selecting the same column twice

Problem 2f: Looks good

Problem 2g: Looks good

Problem 4a:

```{r}

df1 <-Teams |> select(H,AB) |>  mutate(BA=AB-H)
```

Problem 4b:

```{r}
df2 <- Teams |> mutate(SLG = (H + X2B + 2 * X3B + 3 * HR)/AB) |> select(SLG)
```

Problem 4c:

```{r}
df3 <- Teams |> mutate(SLG = (H + X2B + 2 * X3B + 3 * HR)/AB)
ggplot(data = df3) + geom_smooth(aes(x=yearID,y=SLG))
```

Problem 4d:

```{r}
df4 <-Teams |>  mutate(BA=AB-H)
ggplot(data = df4) + geom_smooth(aes(x=yearID,y=BA))
```

Problem 7:

```{r}
#I didn't fully understand what you were asking for on the doc, so I tried to re-create the plot on the doc
df3 <- Teams |> mutate(SLG = (H + X2B + 2 * X3B + 3 * HR)/AB)
ggplot(data = df3) + geom_point(aes(x=yearID,y=SLG)) + geom_smooth(aes(x=yearID,y=SLG))
```
