---
title: "Homework19"
format: html
editor: visual
---

## Joshua L. Kramber - November 7th, 2023 - DST_234 - Homework 19

```{r}
library(tidyverse)
library(maps)
library(mapdata)

cities <- us.cities |>
  data.frame()
```

Question 1a: The variables in this data frame are:

name: has the name of the city plus the abbreviation of the state name

country.etc: abbreviation of the state name

pop: the population of the cities from 2006

lat & long: global coordinates of the city

capital: if the value is 2, the city is a capital. If it is 0, then it's not

Question 1b & c:

```{r}
MNWI <- cities |> filter(country.etc == "WI" | country.etc == "MN")

counties <- map_data("county", region=c('minnesota','wisconsin'))

ggplot(data = counties) + geom_polygon(aes(x = long, y = lat, group = group),fill = "white", color = "black") +
  coord_fixed(1.3) +
  guides(fill="none") + geom_point(data=MNWI,aes(x=long,y=lat,size=pop,color=country.etc)) + labs(title="Cities in MN and WI", x = "Latitude", y = "Longitude",size = "Population", color = "State")
```

Question 2:

```{r}
states <- map_data("state")

state_x77_df <- state.x77 |>
  data.frame() |> 
  rownames_to_column(var="state") |>
  mutate(state=str_to_lower(state))

states_joined <- inner_join(states,state_x77_df,by=c("region"="state")) |>
  filter(region=="minnesota"|region=="wisconsin"|region=="north dakota"|region=="south dakota"|region=="iowa")


ggplot(data = states_joined) + geom_polygon(aes(x = long, y = lat, fill = Population, group = group), color = "black") +
  coord_fixed(1.3) + labs(title="MN, WI, SD, ND, IA Population in 1977", x = "Latitude",y="Longitude")
```

Question 3:

No questions, I appreciate the correction of my title for the mini project 3 though! That was a tough one to put together for me!
